Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-09-06 Docs/IJES/journal.tex
revised version

@@

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, as described by~\cite{Rao2009}, {\it e.g.}, those used in the GA. The only drawback is that the found solution may not be the global minimum or maximum. \textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA.}

@@

\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}.

@@

@@

@@

@@

\bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
MathWorks Inc. (2013) 'MATLAB (version R2013a)'.

@@

@@

\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}.

@@

\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'.

@@

\bibitem[\protect\citeauthoryear{Tranquillo}{2011}]{Tranquillo2011}
Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}.

@@

\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
Wu M., Wu, W., Tai, N., Zhao, H., Fan, J. and Yuan, N. (2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proceedings of the International Conference on Software Engineering and Service Science}, pp.921--924.

\bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
Mittal S., Vetter J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Comput. Surv. 47(4):}, pp. 69:1--69:35.

>>>>

\textcolor{blue}{There is also the effort to create a hardware-software (HW/SW) co-simulation environment in order to help designers obtain an appropriate HW/SW partitioning that satisfy specified tradeoffs, as described by~\cite{Jan2005} and by~\cite{Hau2009}.}

@@

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, as described by~\cite{Rao2009}, {\it e.g.}, those used in the GA. The only drawback is that the found solution may not be the global minimum or maximum. \textcolor{blue}{As relevant studies, ~\cite{Jiang2012} used a GA mixed with simulated annealing and~\cite{Huong2012} designed a modified Pareto optimization using GA. In the other hand, there is some research done to reduce the complexity of computation in order to improve the performance of some techniques, as described by~\cite{Boucheneb2006}.}

@@

\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
Biere, A., Heule, M., Maaren, H. and Walsh, T. (2009) 'Bounded Model Checking', {\it Handbook of Satisfiability}, ISBN 978-1-58603-929-5.

@@

\bibitem[\protect\citeauthoryear{Boucheneb and Hadjidj}{2006}]{Boucheneb2006}
\textcolor{blue}{Boucheneb, H. and Hadjidj, R. (2006) 'Using inclusion abstraction to construct Atomic State Class Graphs for Time Petri Nets', {\it Int. J. of Embedded Systems}, Vol. 2, N. 1/2, pp.128--139.}

@@

\bibitem[\protect\citeauthoryear{Hau and Khalil-Hani}{2009}]{Hau2009}
\textcolor{blue}{Hau, Y.W. and Khalil-Hani, M. (2009) 'SystemC-based HW/SW co-simulation platform for system-on-chip (SoC) design space exploration', {\it Int. J. of Information and Communication Technology}, 2009, Vol.2, N. 1/2, pp.108--119.}

@@

\bibitem[\protect\citeauthoryear{Jan \textit{et al.}}{2005}]{Jan2005}
\textcolor{blue}{Jan, K. Y., Fan, C. B., Kuo, A. C., Yen, W. C., and Lin, Y. L. (2005) 'A platform based SOC design methodology and its application in image compression', {\it Int. J. of Embedded Systems}, Vol.1, N. 1/2, pp. 23--32.}

@@

\bibitem[\protect\citeauthoryear{MathWorks}{2013}]{TheMathWorks2013}
MathWorks Inc. (2013) 'MATLAB (version R2013a)', ISBN 9780982583883.

@@

\bibitem[\protect\citeauthoryear{Mittal \textit{et al.}}{2015}]{Mittal2015}
\textcolor{blue}{Mittal, S., and Vetter, J. (2015) 'A Survey of CPU-GPU Heterogeneous Computing Techniques', {\it ACM Computing Surveys}, Vol. 47, Issue 4, pp. 69:1--69:35.}

@@

\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
Muller, M. (2002) 'OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}.

@@

\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition', ISBN 978-0-470-18352-6.

@@

\bibitem[\protect\citeauthoryear{Tranquillo}{2011}]{Tranquillo2011}
Tranquillo, J. (2011) 'Matlab for Engineering and the Life Sciences', {\it Synthesis Lectures on Engineering. Morgan Claypool}, ISBN 9781608457113.

@@

\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J. and Yuan, N. (2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proceedings of the International Conference on Software Engineering and Service Science}, pp.921--924.
